ms_russia_results

### 2024-06-11 ms-russia-figures.Rmd
update figures ahead of coauthor approval

consumption_russian_ts_fill <- consumption_russian_ts %>%
  ggplot(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_area() +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

@@

species_rank_1 <- species_rank_df %>%
  filter(common_name_hs_modified == "Alaska\nPollock") %>%
  mutate(dom_source == "") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_2 <- species_rank_df %>%
  filter(common_name_hs_modified == "Atlantic\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_3 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pink\nSalmon") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_4 <- species_rank_df %>%
  filter(common_name_hs_modified == "Haddock") %>%
  mutate(common_name_hs_modified = paste("\n", common_name_hs_modified, sep = "")) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_5 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pacific\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  xlim(0, 90) +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    axis.text.x = element_text(size = 7),
    axis.title.x = element_text(size = 7, hjust = 1),
    legend.key.height = unit(3, "mm"),
    legend.key.width = unit(3, "mm"),
    plot.margin = margin(t = -2, b = -1, unit = "mm")
  ) +
  labs(y = "", x = "Avg. Consumption (1000 t) 2015-2019", fill = "")

@@

fig2 <- ggarrange(
  rus_us_sankey,
  fig2,
  nrow = 2,
  heights = c(1, 2)
)

>>>>

consumption_russian_ts_fill <- consumption_russian_ts %>%
  ggplot() +
  geom_area(aes(x = year, y = consumption_live_t/1000000, fill = path)) +
  geom_vline(aes(xintercept = 2014), linetype = 2) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  labs(x = "", y = "Consumption (mil t, live weight)", fill = "") +
  facet_wrap(~sanctions_towards_russia,
             labeller = labeller(group = c(a = "A", b = "B"))) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 9),
    legend.position = "top",
    panel.spacing = unit(5, "mm")
  )

@@

species_rank_1 <- species_rank_df %>%
  filter(common_name_hs_modified == "Alaska\nPollock") %>%
  mutate(dom_source == "") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) +
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_2 <- species_rank_df %>%
  filter(common_name_hs_modified == "Atlantic\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_3 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pink\nSalmon") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_4 <- species_rank_df %>%
  filter(common_name_hs_modified == "Haddock") %>%
  mutate(common_name_hs_modified = paste("\n", common_name_hs_modified, sep = "")) %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  xlim(0, 90) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    plot.margin = margin(b = -2, unit = "mm")
  ) +
  labs(y = "", x = "", fill = "")

species_rank_5 <- species_rank_df %>%
  filter(common_name_hs_modified == "Pacific\nCod") %>%
  plot_bar(bar_group = "common_name_hs_modified", fill_type = "path", top_n = 5) + 
  scale_fill_manual(values = c("#D4B95f", # khaki
                               "#4FA2A2" # teal
  )) + 
  xlim(0, 90) +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(angle = 90, hjust = 0.5),
    axis.text.x = element_text(size = 7),
    axis.title.x = element_text(size = 7, hjust = 1),
    legend.key.height = unit(3, "mm"),
    legend.key.width = unit(3, "mm"),
    plot.margin = margin(t = -2, b = -1, unit = "mm")
  ) +
  labs(y = "", x = "Avg. Consumption (1000 t) 2015-2019", fill = "")

@@

fig2 <- ggarrange(
  rus_us_sankey,
  fig2,
  nrow = 2,
  heights = c(1, 2),
  labels = c("a", "b")
)

### 2024-06-11 ms-russia-results.Rmd
update figures ahead of coauthor approval

```{r load_data}
consumption <- read.csv(file.path(datadir, "case_study_consumption.csv"))
consumption_by_rus <- read.csv(file.path(datadir, "fig1_consumption_by_russia.csv"))
rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
```

@@

```{r consumption_minimums_2020}

alaska_pollock_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "gadus chalcogrammus") %>%
  pull(min_russia)

pink_salmon_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "oncorhynchus gorbuscha") %>%
  pull(min_russia)
```

@@

>>>>

```{r load_data}
consumption <- read.csv(file.path(datadir, "case_study_consumption.csv")) %>%
  mutate(sciname_hs_modified = case_when(
    is.na(sciname_hs_modified) ~ sciname,
    TRUE ~ sciname_hs_modified
  ))

consumption_by_rus <- read.csv(file.path(datadir, "fig1_consumption_by_russia.csv"))

rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))

us_consumption <- read.csv(file.path(datadir, "case_study_usa_consumption.csv")) %>%
  mutate(sciname_hs_modified = case_when(
    is.na(sciname_hs_modified) ~ sciname,
    TRUE ~ sciname_hs_modified
  ))
```

@@

```{r consumption_minimums_2020}
# Min value from Russia
alaska_pollock_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "gadus chalcogrammus") %>%
  pull(min_russia)

pink_salmon_min <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "oncorhynchus gorbuscha") %>%
  pull(min_russia)

# Max value from Russia
alaska_pollock_max <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "gadus chalcogrammus") %>%
  pull(max_russia)

pink_salmon_max <- rus_chn_usa %>%
  filter(year == 2020 &
           sciname == "oncorhynchus gorbuscha") %>%
  pull(max_russia)

us_total_pollock_consumption <- us_consumption %>%
  filter(sciname == "gadus chalcogrammus") %>%
  # Min/max flow values are in 1000 tonnes
  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
  pull(consumption_live_t)

us_imported_pollock_consumption <- us_consumption %>%
  filter(sciname == "gadus chalcogrammus",
         !is.na(exporter_iso3c)) %>%
  # Min/max flow values are in 1000 tonnes
  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
  pull(consumption_live_t)

us_imported_salmon_consumption <- us_consumption %>%
  filter(sciname == "oncorhynchus gorbuscha",
         !is.na(exporter_iso3c)) %>%
  # Min/max flow values are in 1000 tonnes
  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
  pull(consumption_live_t)

us_russian_pollock_consumption <- us_consumption %>%
  filter(sciname == "gadus chalcogrammus",
         !is.na(exporter_iso3c),
         source_country_iso3c == "RUS") %>%
  # Min/max flow values are in 1000 tonnes
  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
  pull(consumption_live_t)

us_russian_salmon_consumption <- us_consumption %>%
  filter(sciname == "oncorhynchus gorbuscha",
         !is.na(exporter_iso3c),
         source_country_iso3c == "RUS") %>%
  # Min/max flow values are in 1000 tonnes
  summarise(consumption_live_t = sum(consumption_live_t) / 1e3) %>%
  pull(consumption_live_t)

us_consumption %>%
  filter(consumer_iso3c == "USA", 
         sciname_hs_modified %in% c("oncorhynchus gorbuscha", "gadus chalcogrammus")) %>%
  mutate(consumption_source = case_when(
    (source_country_iso3c == consumer_iso3c & is.na(exporter_iso3c)) ~ "domestic",
    (source_country_iso3c == consumer_iso3c & !is.na(exporter_iso3c)) ~ "domestic, foreign processed",
    (source_country_iso3c != consumer_iso3c) ~ "foreign"
  )) %>%
  group_by(sciname_hs_modified, consumption_source) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  group_by(sciname_hs_modified) %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t))

# tmp <- us_consumption %>%
#   filter(consumer_iso3c == "USA", 
#          sciname_hs_modified %in% c("oncorhynchus gorbuscha", "gadus chalcogrammus")) %>%
#   group_by(sciname_hs_modified, source_country_iso3c) %>%
#   summarise(consumption_live_t = sum(consumption_live_t)) %>%
#   group_by(sciname_hs_modified) %>%
#   mutate(percent = 100*consumption_live_t/sum(consumption_live_t))

us_consumption %>%
  filter(consumer_iso3c == "USA", 
         sciname_hs_modified == "oncorhynchus gorbuscha") %>%
  mutate(exporter_iso3c = case_when(
    is.na(exporter_iso3c) ~ source_country_iso3c,
    TRUE ~ exporter_iso3c
  )) %>%
  plot_sankey(cols = c("source_country_iso3c", 
                       "exporter_iso3c", 
                       "consumer_iso3c"),
              value = "consumption_live_t")

```

@@

Based on these ranges, we estimate `r signif(100*alaska_pollock_min/us_imported_pollock_consumption, digits = 3)`-`r min(signif(100*alaska_pollock_max/us_imported_pollock_consumption, digits = 3), 100)`% of imported Alaska pollock and `r signif(100*pink_salmon_min/us_imported_salmon_consumption, digits = 3)`-`r min(signif(100*pink_salmon_max/us_imported_salmon_consumption, digits = 3), 100)`% of imported pink salmon is Russian-harvested.
